---
title: "Spiny Lobster Report"
author: "Erica Johnson & Kristan Culbert"
date: "11/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#load libraries
library(tidyverse)
library(kableExtra)
library(effsize)
library(plotly)
library(dplyr)
library(knitr)
library(pwr)
library(vcdExtra)
library(car)
library(onewaytests)


size = read_csv("lobster_size_abundance.csv") %>% 
  filter(SIZE != "-99999", SITE == "AQUE"| SITE == "NAPL"| SITE == "MOHK" | SITE == "IVEE"| SITE == "CARP") # size data is lobster size abundance, filtered out NAs and selected 5 sites needed for report

traps = read_csv("lobster_traps (1).csv") %>% 
  filter(TRAPS !="0", SITE == "AQUE"| SITE == "NAPL"| SITE == "MOHK" | SITE == "IVEE"| SITE == "CARP") 
# filtered out NAs and selected 5 sites needed for report

abundance_traps=read_csv("lobster_abundance_traps_20122017.csv")
# read in a new file that includes total number of lobsters and number of traps at non-MPA sites by site as a function of year
```



```{r echo=FALSE}
#Change lobster size data to tidy data
#for tidy data, use this size_frequency file
size_frequency = read.csv("lobster_size_abundance.csv", header = TRUE) %>% 
  filter(SIZE != "-99999", SITE == "AQUE"| SITE == "NAPL"| SITE == "MOHK" | SITE == "IVEE"| SITE == "CARP")
#header = TRUE only works with "read.csv". 

size_case = expand.dft(size_frequency, freq = "COUNT")
#This code only works if "header = TRUE" is put into the read.csv (note no "_") code.
```


1. Lobster abundance and fishing pressure (2012 - 2017)
Describe trends in lobster abundance (counts) and fishing pressure (trap buoys) at the five locations from 2012 - 2017. Ignore transect information - we are only interested in evaluating abundance and pressure on the order of SITE. Note: you are not expected to use regression here - just think of ways to clearly describe annual totals visually and in text, noting important trends, events and differences.
```{r echo=FALSE}

#summary table for display. table needs to be expanded
summary_non_mpa_size = size%>% 
  group_by(YEAR, SITE) %>% 
  filter(SITE == "AQUE"| SITE == "CARP"|SITE == "MOHK") %>% 
  count(SITE) %>% 
  spread(YEAR,n)
    

  
 


kable(summary_non_mpa_size, caption ="LTER SBC lobster abundance by non-mpa site, 2012- 2017") %>% 
    kable_styling(bootstrap_option = c("striped", "hover"), full_width = FALSE)


```

```{r echo=FALSE}
#summary table for display. table needs to be expanded
summary_traps = traps%>% 
  group_by(YEAR, SITE) %>% 
  count(SITE) %>% 
  spread(YEAR,n)

kable(summary_traps, caption ="LTER SBC lobster traps by site, 2012- 2017", booktabs= T) %>% 
    kable_styling(bootstrap_option = c("striped", "hover"), full_width = FALSE)


```



```{r echo=FALSE}

#Plot lobster abundance and fishing pressure in non-mpa sites

ggplot(abundance_traps)+
  geom_line(aes(x=year, y=lobster, col= "Lobsters"))+
  geom_line(aes(x=year, y= traps, col= "Traps"))+
  facet_wrap(~site)+
  labs(y="Lobster Abundance (n)", x= "Year", col= "Key") +
scale_y_continuous(sec.axis = sec_axis(~., name = "Lobster Traps (n)")) +
theme_classic()+
  theme(axis.text.x=element_text(angle=60, hjust=1))
  ggtitle("Lobster Abundance and Fishing Pressure in SBC LTER Non-MPA sites, 2012-2017")


```

```{r echo=FALSE}
# lobster summary for mpa sites only
size_mpa = size%>% 
  group_by(YEAR, SITE) %>% 
  filter(SITE == "NAPL"|SITE == "IVEE")

 sum_mpa = summarize(size_mpa,COUNT = round(sum(COUNT),2))

 

#Plot lobster abundance in mpa sites, no fishing pressure

ggplot(sum_mpa)+
  geom_line(aes(x=YEAR, y=(COUNT), col= "Lobsters"))+
  labs(y="Lobster Abundance (n)", x= "Year", col= "Key")+
  theme_classic()+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  ggtitle("Lobster Abundance SBC LTER MPA sites, 2012-2017")+
  facet_wrap(~SITE)
```


```{r include=FALSE}
#data exploration, lobster carapace size

size_non_mpa = size %>% filter(SITE == "AQUE"| SITE == "CARP"|SITE == "MOHK")

ggplot(size, aes(x=SIZE))+
  geom_histogram()+
  facet_wrap(~SITE)

ggplot(size, aes(sample=SIZE))+
  geom_qq()+
  facet_wrap(~SITE)


```



2. Compare mean lobster size by site in 2017
Compare mean lobster sizes (carapace length (mm)) across the five sites for lobster observations collected in 2017. 
```{r echo=FALSE}

#summary table of lobster size

size_2017 = size_case %>% 
  filter(SIZE != "-99999", YEAR == 2017) %>% 
  group_by(SITE)
        
summary_size_2017 = summarize(size_2017,
            "Median (mm)" = round(median(SIZE),2),
            "Maximum (mm)" = max(SIZE),
            "Mean (mm)" = round (mean(SIZE),2),
            "SD (mm)" = round(sd(SIZE),2),
            "Sample size (n)" = length(unique(SIZE)),
            "Variance" = round(var(SIZE),2) #test for equal variance
    )
#General rule: if the greatest variances is < 4x bigger than the smallest variance, then usually those are "close enough" to assume equal variance

kable(summary_size_2017, caption ="LTER SBC mean lobster carapace length (mm) by site in 2017, n = 1668") %>% 
    kable_styling(bootstrap_option = c("striped", "hover"), full_width = FALSE)


```

```{r}

#Variances are close- largest variance is not 4x  > smallest variance.

#One-Way Anova:

lobster_aov = aov(SIZE ~ SITE, data = size_2017)
lobster_aov

TukeyHSD(lobster_aov)

```

```{r}

```

3. Changes in lobster size at MPA and non-MPA sites (comparing only 2012 and 2017 sizes)

From the data description (http://sbc.lternet.edu/cgi-bin/showDataset.cgi?docid=knb-lter-sbc.77): 

“Data on abundance, size and fishing pressure of California spiny lobster (Panulirus interruptus) are collected along the mainland coast of the Santa Barbara Channel. Spiny lobsters are an important predator in giant kelp forests off southern California. 

Two SBC LTER study reefs are located in or near the California Fish and Game Network of Marine Protected Areas (MPA), Naples
and Isla Vista, both established as MPAs on 2012-01-01. MPAs provide a unique opportunity to
investigate the effects of fishing on kelp forest community dynamics. Sampling began in 2012 and
is ongoing.” 

At Isla Vista and Naples Reef, the two protected MPA sites (with zero fishing pressure), how do lobster sizes in 2012 and 2017 compare? At the non-MPA sites?
```{r}

# Kristan: need to create data frames for 2012 MPA, 2012 non-MPA, 2017 MPA and 2017 non-MPA data, then run an ANOVA (to compare means?)
size_2012_2017_non = size_non_mpa %>% 
  filter(SIZE != "-99999", YEAR == 2012|YEAR == 2017) %>% 
  group_by(SITE)

size_2012_2017_mpa = size_mpa %>% 
  filter(SIZE != "-99999", YEAR == 2012|YEAR == 2017) %>% 
  group_by(SITE)

ggplot(size_2012_2017_non, aes(x=SIZE))+
  geom_histogram(aes(col =SITE))+
  facet_wrap(~YEAR)+
  theme_classic()

ggplot(size_2012_2017_mpa, aes(x=SIZE))+
  geom_histogram(aes(col =SITE))+
  facet_wrap(~YEAR)+
  theme_classic()


```


4. Proportions of “legal” lobsters at the 5 sites in 2017

The legal minimum carapace size for lobster is 82.6 mm. What proportion of observed lobsters at each site are above the legal minimum? 

Does that proportion differ significantly across the 5 sites? 

Note: Use the chisq.test() function
```{r}

```

