---
title: "spiny-lobster-report"
author: "Erica Johnson"
date: "11/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
library(tidyverse)
library(kableExtra)
library(effsize)
library(plotly)
library(plyr)
library(dplyr)
library(knitr)
library(pwr)
library(vcdExtra)

size = read_csv("lobster_size_abundance.csv")
traps = read_csv("lobster_traps (1).csv")
```
Change lobster sive data to tidy data
```{r}
size_frequency = read.csv("lobster_size_abundance.csv", header = TRUE)
#header = TRUE only works with "read.csv". 
size_case = expand.dft(size, freq = "COUNT")
#This code only works if "header = TRUE" is put into the read.csv (note no "_") code.
```


1. Lobster abundance and fishing pressure (2012 - 2017)
Describe trends in lobster abundance (counts) and fishing pressure (trap buoys) at the five locations from
2012 - 2017. Ignore transect information - we are only interested in evaluating abundance and pressure on the
order of SITE. Note: you are not expected to use regression here - just think of ways to clearly
describe annual totals visually and in text, noting important trends, events and differences.
```{r}

```


2. Compare mean lobster size by site in 2017
Compare mean lobster sizes (carapace length (mm)) across the five sites for lobster observations collected in
2017. Warning: the size data are not in tidy format. There are rows that contain size information for multiple
lobsters observed (e.g., if the researcher saw 3 lobsters all with carapace length ~ 60 mm, then they will have a
single row where COUNT = 3 and SIZE = 60). You’ll want to get this into case format - where each lobster
has its own row - before doing statistical analyses. There are many ways to do this. One hint: function
expand.dft in the vcdExtra package (it doesn’t like tibbles, so you might need to coerce to data.frame first).
```{r}

```

3. Changes in lobster size at MPA and non-MPA sites (comparing only 2012 and 2017 sizes)
From the data description (http://sbc.lternet.edu/cgi-bin/showDataset.cgi?docid=knb-lter-sbc.77):
“Data on abundance, size and fishing pressure of California spiny lobster (Panulirus interruptus)
are collected along the mainland coast of the Santa Barbara Channel. Spiny lobsters are an
important predator in giant kelp forests off southern California. Two SBC LTER study reefs are
located in or near the California Fish and Game Network of Marine Protected Areas (MPA), Naples
and Isla Vista, both established as MPAs on 2012-01-01. MPAs provide a unique opportunity to
investigate the effects of fishing on kelp forest community dynamics. Sampling began in 2012 and
is ongoing.”
At Isla Vista and Naples Reef, the two protected MPA sites (with zero fishing pressure), how do lobster sizes
in 2012 and 2017 compare? At the non-MPA sites?
```{r}

```
4. Proportions of “legal” lobsters at the 5 sites in 2017
The legal minimum carapace size for lobster is 82.6 mm. What proportion of observed lobsters at each site
are above the legal minimum? Does that proportion differ significantly across the 5 sites? Note: We’ll be
doing chi-square in labs next week, or go ahead with maximum resourcefulness and check out the chisq.test()
function on your own!
```{r}

```

